Generalized Bradley-Terry models

### 2025-02-21 inst/jss_hyper3_real.Rnw
more tweaking

Implementation in \code{hyper3} formalism is straightforward.  Object
\code{sushi\_eq\_class} specifies the two equivalence classes

<<show_sushi_eq_classes>>=
sushi_eq_classes
head(noquote(sushi_table))
@

We can now use this to define a bespoke likelihood function, using
$\lambda$ as  the argument:

@@

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=3,len=2)
L <- sapply(s,f)
@

<<plotsushi>>=
plot(s,L-max(L),type='b')
@

>>>>

Implementation in \code{hyper3} formalism is straightforward.  The
dataset used is \code{sushi\_table}, part of the \code{hyper2} package:

<<showsushitable>>=
head(noquote(sushi_table))
@

Thus, from the top line, we see that the first judge placed tamago
first, followed by anago and ika.  The equivalence classes are given
by

<<show_sushi_eq_classes>>=
sushi_eq_classes
@

so class 2 is the tuna group and class 1 everything else.  We can now
use these datapoint to define a bespoke likelihood function, using
$\lambda$ as the argument:

@@

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- exp(seq(from = log(0.9), to = log(10), len = 12))
L <- sapply(s,f)
@

<<plotsushi>>=
plot(log(s),L-max(L),type='b',xlab=expression(log(lambda)), ylab='Log-likelihood')
@
